---
title: "data collection and processing"
author: "JJayes"
date: "01/07/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(httr)
library(glue)

```

# Purpose

Get the data and make it nice and tidy.

## Structure

Query API for Youtube to get the information about the videos and the descriptions from the Needle Drop album reviews.

We need to get a list of all of the uploads.

Then we need to filter these to get only the album reviews.

## Start with quarying API for channel content

I plan to rewrite this section into tidy format.

```{r}
key <- "AIzaSyBHGmTJ2uLeMsIjBUN3jN7G3RSjozkaq8k"
user_id <- "theneedledrop"  # Username
base <- "https://www.googleapis.com/youtube/v3/"
```

```{r}
# Construct the API call
api_params <- 
  paste(paste0("key=", key), 
        paste0("forUsername=", user_id), 
        "part=snippet,contentDetails,statistics",
        sep = "&")

api_call <- paste0(base, "channels", "?", api_params)
api_result <- GET(api_call)
json_result <- content(api_result, "text", encoding="UTF-8")
```

```{r}
# Process the raw data into a data frame
channel.json <- fromJSON(json_result, flatten = T)
channel.df <- channel.json$items %>% as_tibble()

# get playlist id for uploads
channel.df %>% 
    select(contentDetails.relatedPlaylists.uploads)

playlist_id <- channel.df %>% 
    select(contentDetails.relatedPlaylists.uploads) %>% as.character()
```

Get all videos from uploads, call it upload.df.

```{r}
# temporary variables
nextPageToken <- ""
upload.df <- NULL
pageInfo <- NULL
# Loop through the playlist while there is still a next page
while (!is.null(nextPageToken)) {
  # Construct the API call
  api_params <- 
    paste(paste0("key=", key), 
          paste0("playlistId=", playlist_id), 
          "part=snippet,contentDetails,status",
          "maxResults=50",
          sep = "&")
  
  # Add the page token for page 2 onwards
  if (nextPageToken != "") {
    api_params <- paste0(api_params,
                         "&pageToken=",nextPageToken)
  }
  
  api_call <- paste0(base, "playlistItems", "?", api_params)
  api_result <- GET(api_call)
  json_result <- content(api_result, "text", encoding="UTF-8")
  upload.json <- fromJSON(json_result, flatten = T)
  
  nextPageToken <- upload.json$nextPageToken
  pageInfo <- upload.json$pageInfo
  
  curr.df <- as.data.frame(upload.json$items)
  if (is.null(upload.df)) {
    upload.df <- curr.df
  } else {
    upload.df <- bind_rows(upload.df, curr.df)
  }
}

upload_tbl <- upload.df %>% as_tibble()

# upload_tbl %>% head() %>% view()
```

### Get data about each video from the API.

Get the ID (I call it `video_id`) for each video from the URL of the thumbnails that was returned in the uploads query.

```{r}
tbl <- upload_tbl

tbl <- tbl %>%
  mutate(video_id = str_remove(snippet.thumbnails.default.url, "https://i.ytimg.com/vi/"),
         video_id = str_remove(video_id, "/default.jpg"))
```

Function to get data about the video from the API.

```{r}
get_video_data <- function(video_id){
  
  base <- "https://www.googleapis.com/youtube/v3/"
  
  key <- "AIzaSyBHGmTJ2uLeMsIjBUN3jN7G3RSjozkaq8k"
  
  part <- "part=id,statistics,contentDetails,snippet"
  
  api_call <- 
    glue::glue(base,
         "videos?",
         part,
         "&",
         "id=",
         video_id,
         "&",
         "key=",key)
  # GET the API call
  api_result <- httr::GET(api_call)
  # get the result in a JSON format
  json_result <- httr::content(api_result, "text", encoding="UTF-8")
  # flatten result
  json_result_flat <- jsonlite::fromJSON(json_result, flatten = T)
  # get only what we care about from the call. These are stored in the items list
  results <- json_result_flat$items
  # the tags are a list and we want to get them into a comma seperated character variable.
  tags <- json_result_flat$items$snippet.tags[[1]] %>% toString() %>% as_tibble() %>% rename(tags = value)
  # get just the other items
  results <- results %>% dplyr::as_tibble() %>% 
    select(-snippet.tags)
  # stick them together.
  results <- results %>% bind_cols(tags)
 
  results    
  
}

# test <- get_video_data("6kWWLOampOM")
```

Map the video ids across the new function, for only the videos that are album reviews.

```{r}
list_of_album_reviews <- tbl %>% 
  select(video_id, snippet.title) %>% 
  filter(str_detect(snippet.title, "ALBUM REVIEW"))

album_reviews <- list_of_album_reviews %>% 
  # look at this cool map function! 
  mutate(video_data = map(video_id, get_video_data))

album_reviews <- album_reviews %>% 
  select(-snippet.title) %>% 
  unnest(video_data)

# write_rds(album_reviews, "data/album_reviews_raw_added_tags.rds")
```

### Transcripts

I moved to python to get the transcripts and join them together. I'll link the jupyter notebook here at some point. It's a bit janky.

### Reading in data for processing

```{r}
tbl <- read_rds("data/transcripts_filtered_and_data.rds")

tbl <- tbl %>% 
    select(video_id,
           snippet.title,
           snippet.publishedAt,
           snippet.description,
           contentDetails.duration,
           starts_with("statistics"),
           tags,
           text) %>% 
    select(-statistics.favoriteCount)

```

Some reviews (176) didn't get captions from the captions API. 

```{r}
tbl %>%
    count(text, sort = T)
```


```{r}
tbl <- tbl %>% 
    # problem is the missing texts
  mutate(text = str_remove(text, "A n e x c e p t i o n o c c u r r e d"),
           text = na_if(text, "")) %>% 
  # the \n before it is to correct for the song called 10/10 by Rex Orange County
  mutate(score_raw = str_extract(snippet.description, "\n[0-9]/10|\n10/10|CLASSIC"),
         # numeric score
         score = parse_number(score_raw),
         # date
         published_date = lubridate::date(snippet.publishedAt),
         # duration as numeric
         duration = lubridate::duration(contentDetails.duration),
         # numeric across the statistics
         across(starts_with("statistics"), fn = ~ as.numeric(.)),
         url = str_c("https://www.youtube.com/watch?v=", video_id)) %>% 
    # nice variable names
    janitor::clean_names() %>% 
    select(-snippet_published_at, -content_details_duration) %>% 
    rename_with(~ str_replace(.x, "snippet", "video")) %>% 
    rename_with(~ str_replace(.x, "statistics", "video_statistics")) %>% 
    # put score first
    relocate(score, .before = video_id)

# removing strangs things from text in tags.
tbl <- tbl %>% 
  mutate(tags = str_remove_all(tags, "rvwz"))

# write_rds(tbl, "data/clean_data_1_july.rds")
```

### Now i want to get the data from the spotify API about the music.

Following advice from [this article](https://medium.com/swlh/accessing-spotifys-api-using-r-1a8eef0507c) on how to access the spotify API.



```{r}

id <- "2a85e163bc1d4deeb6569f6e2aff09cf"
secret <- "3ce40c489719404db703462447d58616"

response = POST(
  'https://accounts.spotify.com/api/token',
  accept_json(),
  authenticate(id, secret),
  body = list(grant_type = 'client_credentials'),
  encode = 'form',
  verbose()
)
mytoken = content(response)$access_token
HeaderValue = glue("Bearer ", mytoken)

```

We need to start by getting artist and album ids.

```{r}
df %>% 
    select(video_title)

df <- df %>% 
    mutate(video_artist = str_extract(video_title, ".*-"),
           video_artist = str_squish(str_remove(video_artist, "-")),
           video_album_query = str_squish(str_remove(video_title, "ALBUM REVIEW")))

df %>% select(video_title, video_artist, video_album_query) %>% tail(10)
```

Function to get artist data

```{r}
get_artist_data <- function(video_artist){
  
  base <- "https://api.spotify.com/v1/search?q="
  
  params <- "&type=artist&market=GB&limit=1"
  
  artist_name_url_encoded <- video_artist %>% URLencode()
  
  # call consists of uri = base + artist name as string + params
  api_call <- glue::glue(
         base,
         artist_name_url_encoded,
         params)
  # GET the API call
  api_result <- httr::GET(api_call, add_headers(Authorization = HeaderValue), 
                                    add_headers("Accept: application/json"),
                                    add_headers("Content-Type: application/json"))
  
  # get the result in a JSON format
  json_result <- httr::content(api_result, "text", encoding="UTF-8")
  # flatten result
  json_result_flat <- jsonlite::fromJSON(json_result, flatten = T)
  
  # collect name, id, popularity, genres, followers, data. 
  # name is just a check to make sure that it is the same as from the reviews
  spotify_artist_name <- json_result_flat$artists$items$name
  
  spotify_artist_id <- json_result_flat$artists$items$id
  
  spotify_artist_popularity <- json_result_flat$artists$items$popularity

  spotify_artist_genres <- json_result_flat$artists$items$genres[[1]] %>% toString()
  
  spotify_artist_followers <- json_result_flat$artists$items$followers.total
  
  spotify_artist_data <- tibble(spotify_artist_name,
                                spotify_artist_id, 
                                spotify_artist_genres,
                                spotify_artist_popularity, 
                                spotify_artist_followers)
  
  spotify_artist_data
}

# test <- get_artist_data("Jacob Collier")

```

Album information from name

```{r}

"Tyler%2C%20the%20Creator%20Call%20Me%20If%20You%20Get%20Lost&type=album"
```

```{r}
video_album <- "King Gizzard & The Lizard Wizard - Butterfly 3000"

get_album_id <- function(video_album_query){
  
  base <- "https://api.spotify.com/v1/search?q="
  
  params <- "&type=album&market=GB&limit=1"
  
  album_url_encoded <- video_album_query %>% URLencode()
  
  # call consists of uri = base + artist name as string + params
  api_call <- glue::glue(
         base,
         album_url_encoded,
         params)
  # GET the API call
  api_result <- httr::GET(api_call, add_headers(Authorization = HeaderValue), 
                                    add_headers("Accept: application/json"),
                                    add_headers("Content-Type: application/json"))
  
  # get the result in a JSON format
  json_result <- httr::content(api_result, "text", encoding="UTF-8")
  # flatten result
  json_result_flat <- jsonlite::fromJSON(json_result, flatten = T)
  
  # collect name, id, popularity, genres, followers, data. 
  # name is just a check to make sure that it is the same as from the reviews
  spotify_album_name <- json_result_flat$albums$items$name
  
  spotify_album_id <- json_result_flat$albums$items$id
  
  spotify_album_release_date <- json_result_flat$albums$items$release_date

  spotify_album_n_tracks <- json_result_flat$albums$items$total_tracks
  
  spotify_album_data <- tibble(spotify_album_name,
                                spotify_album_id, 
                                spotify_album_release_date,
                                spotify_album_n_tracks)
  
  spotify_album_data
}

test <- get_album_id("Tyler, the Creator - Flower Boy")

```

Album information from id

```{r}

spotify_album_id <- "2nkto6YNI4rUYTLqEwWJ3o"

get_album_data <- function(spotify_album_id){
  
  base <- "https://api.spotify.com/v1/albums/"
  
  params <- "/tracks"
  
  # call consists of uri = base + artist name as string + params
  api_call <- glue::glue(
         base,
         spotify_album_id,
         params)
  # GET the API call
  api_result <- httr::GET(api_call, add_headers(Authorization = HeaderValue), 
                                    add_headers("Accept: application/json"),
                                    add_headers("Content-Type: application/json"))
  
  # get the result in a JSON format
  json_result <- httr::content(api_result, "text", encoding="UTF-8")
  # flatten result
  json_result_flat <- jsonlite::fromJSON(json_result, flatten = T)
  
  track_name <- json_result_flat$items$name
  
  track_id <- json_result_flat$items$id
  
  track_explicit <- json_result_flat$items$explicit
  
  spotify_track_data <- tibble(track_name,
                               track_id, 
                               track_explicit)

  spotify_track_data
}
```

Now to get song information and audio features

```{r}

track_id <- "6KuXb26rHuRy3ZDse1VRmx"

get_song_audio_features <- function(track_id){
  
  base <- "https://api.spotify.com/v1/audio-features/"
  
  # call consists of uri = base + song id as string
  api_call <- glue::glue(
         base,
         track_id)
  # GET the API call
  api_result <- httr::GET(api_call, add_headers(Authorization = HeaderValue), 
                                    add_headers("Accept: application/json"),
                                    add_headers("Content-Type: application/json"))
  
  # get the result in a JSON format
  json_result <- httr::content(api_result, "text", encoding="UTF-8")
  # flatten result
  json_result_flat <- jsonlite::fromJSON(json_result, flatten = T)
  
  track_data <- json_result_flat %>% as_tibble() %>% select(danceability:tempo, duration_ms:time_signature)
  
  spotify_track_data <- tibble(track_name,
                               track_id, 
                               track_explicit)

  spotify_track_data
}

```


