---
title: "data collection and processing"
author: "JJayes"
date: "01/07/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(httr)
library(glue)
library(jsonlite)
```

# Purpose

Get the data and make it nice and tidy.

## Structure

Query API for Youtube to get the information about the videos and the descriptions from the Needle Drop album reviews.

We need to get a list of all of the uploads.

Then we need to filter these to get only the album reviews.

## Start with quarying API for channel content

I plan to rewrite this section into tidy format.

```{r}
key <- "AIzaSyBHGmTJ2uLeMsIjBUN3jN7G3RSjozkaq8k"
user_id <- "theneedledrop"  # Username
base <- "https://www.googleapis.com/youtube/v3/"
```

```{r}
# Construct the API call
api_params <- 
  paste(paste0("key=", key), 
        paste0("forUsername=", user_id), 
        "part=snippet,contentDetails,statistics",
        sep = "&")

api_call <- paste0(base, "channels", "?", api_params)
api_result <- GET(api_call)
json_result <- content(api_result, "text", encoding="UTF-8")
```

```{r}
# Process the raw data into a data frame
channel.json <- fromJSON(json_result, flatten = T)
channel.df <- channel.json$items %>% as_tibble()

# get playlist id for uploads
channel.df %>% 
    select(contentDetails.relatedPlaylists.uploads)

playlist_id <- channel.df %>% 
    select(contentDetails.relatedPlaylists.uploads) %>% as.character()
```

Get all videos from uploads, call it upload.df.

```{r}
# temporary variables
nextPageToken <- ""
upload.df <- NULL
pageInfo <- NULL
# Loop through the playlist while there is still a next page
while (!is.null(nextPageToken)) {
  # Construct the API call
  api_params <- 
    paste(paste0("key=", key), 
          paste0("playlistId=", playlist_id), 
          "part=snippet,contentDetails,status",
          "maxResults=50",
          sep = "&")
  
  # Add the page token for page 2 onwards
  if (nextPageToken != "") {
    api_params <- paste0(api_params,
                         "&pageToken=",nextPageToken)
  }
  
  api_call <- paste0(base, "playlistItems", "?", api_params)
  api_result <- GET(api_call)
  json_result <- content(api_result, "text", encoding="UTF-8")
  upload.json <- fromJSON(json_result, flatten = T)
  
  nextPageToken <- upload.json$nextPageToken
  pageInfo <- upload.json$pageInfo
  
  curr.df <- as.data.frame(upload.json$items)
  if (is.null(upload.df)) {
    upload.df <- curr.df
  } else {
    upload.df <- bind_rows(upload.df, curr.df)
  }
}

upload_tbl <- upload.df %>% as_tibble()

# upload_tbl %>% head() %>% view()
```

### Get data about each video from the API.

Get the ID (I call it `video_id`) for each video from the URL of the thumbnails that was returned in the uploads query.

```{r}
tbl <- upload_tbl

tbl <- tbl %>%
  mutate(video_id = str_remove(snippet.thumbnails.default.url, "https://i.ytimg.com/vi/"),
         video_id = str_remove(video_id, "/default.jpg"))
```

Function to get data about the video from the API.

```{r}
video_id <- "Ppn7Km1v7pA"

get_video_data <- function(video_id){
  message("Getting data from ", video_id)
  
  base <- "https://www.googleapis.com/youtube/v3/"
  
  key <- "AIzaSyBHGmTJ2uLeMsIjBUN3jN7G3RSjozkaq8k"
  
  part <- "part=id,statistics,contentDetails,snippet"
  
  api_call <- 
    glue::glue(base,
         "videos?",
         part,
         "&",
         "id=",
         video_id,
         "&",
         "key=",key)
  # GET the API call
  api_result <- httr::GET(api_call)
  # get the result in a JSON format
  json_result <- httr::content(api_result, "text", encoding="UTF-8")
  # flatten result
  json_result_flat <- jsonlite::fromJSON(json_result, flatten = T)
  # get only what we care about from the call. These are stored in the items list
  results <- json_result_flat$items
  # the tags are a list and we want to get them into a comma seperated character variable.
  tags <- json_result_flat$items$snippet.tags[[1]] %>% 
    paste(collapse = "\n") %>%
    as_tibble() %>% rename(tags = value)
  # get just the other items
  results <- results %>% dplyr::as_tibble() %>% 
    select(-snippet.tags)
  # stick them together.
  results <- results %>% bind_cols(tags)
 
  results 
  
}

# test <- get_video_data("6kWWLOampOM")
```

Map the video ids across the new function, for only the videos that are album reviews.

```{r}
list_of_album_reviews <- tbl %>% 
  select(video_id, snippet.title) %>% 
  filter(str_detect(snippet.title, "ALBUM REVIEW"))

album_reviews <- list_of_album_reviews %>% 
  # look at this cool map function! 
  mutate(video_data = map(video_id, get_video_data))

album_reviews <- album_reviews %>% 
  select(-snippet.title) %>% 
  unnest(video_data)

# write_rds(album_reviews, "data/album_reviews_raw_added_tags_2.rds")

# album_reviews %>%
#   # filter(contentDetails.caption == "true") %>%
#   select(video_id) %>%
#   write.csv("data/video_ids_2022.csv")

```

### Transcripts

I moved to python to get the transcripts and join them together. I'll link the jupyter notebook here at some point. It's a bit janky.

Maybe I try with another package in R

```{r}
library("youtubecaption")

album_reviews <- readRDS("data/album_reviews_raw_added_tags_2.rds")

captions <- album_reviews %>% 
  select(video_id)

captions_head <- captions %>% 
  head()

captions_head %>% 
  mutate(caption = get_caption(video_id))
```


### Reading in data for processing

```{r}
tbl <- read_rds("data/transcripts_filtered_and_data.rds")

tbl <- tbl %>% 
    select(video_id,
           snippet.title,
           snippet.publishedAt,
           snippet.description,
           snippet.thumbnails.standard.url,
           contentDetails.duration,
           starts_with("statistics"),
           tags,
           text) %>% 
    select(-statistics.favoriteCount)

```

Some reviews (176) didn't get captions from the captions API. 

```{r}
tbl %>%
    count(text, sort = T)
```


```{r}
tbl <- tbl %>% 
    # problem is the missing texts
  mutate(text = str_remove(text, "A n e x c e p t i o n o c c u r r e d"),
           text = na_if(text, "")) %>% 
  # the \n before it is to correct for the song called 10/10 by Rex Orange County
  mutate(score_raw = str_extract(snippet.description, "\n[0-9]/10|\n10/10|CLASSIC"),
         # numeric score
         score = parse_number(score_raw),
         # date
         published_date = lubridate::date(snippet.publishedAt),
         # duration as numeric
         video_duration = lubridate::duration(contentDetails.duration),
         # numeric across the statistics
         across(starts_with("statistics"), fn = ~ as.numeric(.)),
         url = str_c("https://www.youtube.com/watch?v=", video_id)) %>% 
    # nice variable names
    janitor::clean_names() %>% 
    select(-snippet_published_at, -content_details_duration) %>% 
    rename_with(~ str_replace(.x, "snippet", "video")) %>% 
    rename_with(~ str_replace(.x, "statistics", "video_statistics")) %>% 
    # put score first
    relocate(score, .before = video_id)

# removing strangs things from text in tags.
tbl <- tbl %>% 
  mutate(tags = str_remove_all(tags, "rvwz"))

# write_rds(tbl, "data/clean_data_no_transcript_3_June.rds")
```

### Now i want to get the data from the spotify API about the music.

Following advice from [this article](https://medium.com/swlh/accessing-spotifys-api-using-r-1a8eef0507c) on how to access the spotify API.

```{r}

id <- "2a85e163bc1d4deeb6569f6e2aff09cf"
secret <- "3ce40c489719404db703462447d58616"

response = POST(
  'https://accounts.spotify.com/api/token',
  accept_json(),
  authenticate(id, secret),
  body = list(grant_type = 'client_credentials'),
  encode = 'form',
  verbose()
)
mytoken = content(response)$access_token
HeaderValue = glue("Bearer ", mytoken)

```

We need to start by getting artist and album ids.

```{r}
df %>% 
    select(video_title)

df <- df %>% 
    mutate(video_album_query = str_squish(str_remove(video_title, "ALBUM REVIEW")))

df %>% select(video_title, video_album_query) %>% tail(10)
```

Album information from name

```{r}
video_album_query <- "Greta Van Fleet - The Battle at Garden's Gate"

get_album_id <- function(video_album_query){
  
  base <- "https://api.spotify.com/v1/search?q="
  
  params <- "&type=album&market=GB&limit=1"
  
  album_url_encoded <- video_album_query %>% URLencode()
  
  message(glue("Getting album data about {video_album_query}"))
  
  # call consists of uri = base + artist name as string + params
  api_call <- glue::glue(
         base,
         album_url_encoded,
         params)
  # GET the API call
  api_result <- httr::GET(api_call, add_headers(Authorization = HeaderValue), 
                                    add_headers("Accept: application/json"),
                                    add_headers("Content-Type: application/json"))
  
  # get the result in a JSON format
  json_result <- httr::content(api_result, "text", encoding="UTF-8")
  # flatten result
  json_result_flat <- jsonlite::fromJSON(json_result, flatten = T)
    # collect name, id, popularity, genres, followers, data. 
  # name is just a check to make sure that it is the same as from the reviews
  spotify_artist_name <- json_result_flat$albums$items$artists[[1]] %>% 
      as_tibble() %>% head(1) %>% select(name) %>% as.character()
  
  spotify_artist_id <- json_result_flat$albums$items$artists[[1]] %>% 
      as_tibble() %>% head(1) %>% select(id) %>% as.character()
  
  spotify_album_name <- json_result_flat$albums$items$name
  
  spotify_album_id <- json_result_flat$albums$items$id
  
  spotify_album_release_date <- json_result_flat$albums$items$release_date

  spotify_album_n_tracks <- json_result_flat$albums$items$total_tracks
  
  spotify_album_data <- tibble(spotify_artist_name,
                               spotify_artist_id,
                               spotify_album_name,
                               spotify_album_id, 
                               spotify_album_release_date,
                               spotify_album_n_tracks)
  spotify_album_data
}

# test <- get_album_id("Greta Van Fleet - The Battle at Garden's Gate")

```

Function to get artist data using artist id

```{r}
spotify_artist_id <- "7A8S43ryYdbWpJKeHRZRcq"

get_artist_data <- function(spotify_artist_id){
  
  base <- "https://api.spotify.com/v1/artists/"
  
  message(glue("Getting artist data from {spotify_artist_id}"))
  
  # call consists of uri = base + artist name as string + params
  api_call <- glue::glue(
         base,
         spotify_artist_id)
  # GET the API call
  api_result <- httr::GET(api_call, add_headers(Authorization = HeaderValue), 
                                    add_headers("Accept: application/json"),
                                    add_headers("Content-Type: application/json"))
  
  # get the result in a JSON format
  json_result <- httr::content(api_result, "text", encoding="UTF-8")
  # flatten result
  json_result_flat <- jsonlite::fromJSON(json_result, flatten = T)
  
  # collect name, id, popularity, genres, followers, data. 
  # name is just a check to make sure that it is the same as from the reviews
  spotify_artist_popularity <- json_result_flat$popularity

  spotify_artist_genres <- json_result_flat$genres %>% paste(collapse = "/n")
  
  spotify_artist_followers <- json_result_flat$followers$total
  
  spotify_artist_data <- tibble(spotify_artist_genres,
                                spotify_artist_popularity, 
                                spotify_artist_followers)
  
  spotify_artist_data
}

test <- get_artist_data(spotify_artist_id)

```

Album information from id. The results will be stored as a string, in most cases separated with a semicolon, except for the ids which will be sep with comma for use later.

```{r}

spotify_album_id <- "2nkto6YNI4rUYTLqEwWJ3o"

get_album_data <- function(spotify_album_id){
  
  base <- "https://api.spotify.com/v1/albums/"
  
  params <- "/tracks"
  
  message(glue("Getting album data from {spotify_album_id}"))
  
  # call consists of uri = base + artist name as string + params
  api_call <- glue::glue(
         base,
         spotify_album_id,
         params)
  # GET the API call
  api_result <- httr::GET(api_call, add_headers(Authorization = HeaderValue), 
                                    add_headers("Accept: application/json"),
                                    add_headers("Content-Type: application/json"))
  
  # get the result in a JSON format
  json_result <- httr::content(api_result, "text", encoding="UTF-8")
  # flatten result
  json_result_flat <- jsonlite::fromJSON(json_result, flatten = T)
  
  track_name <- json_result_flat$items$name
  
  track_id <- json_result_flat$items$id
  
  track_explicit <- json_result_flat$items$explicit
  
  spotify_track_data <- tibble(track_name,
                               track_id, 
                               track_explicit)

  spotify_track_data
}

get_album_data("2nkto6YNI4rUYTLqEwWJ3o")
```

Now to get song information and audio features

```{r}

track_id <- "6KuXb26rHuRy3ZDse1VRmx"

get_track_features <- function(track_id){
  
  base <- "https://api.spotify.com/v1/audio-features/"
  
  message(glue("Getting audio features from {track_id}"))
  
  # call consists of uri = base + song id as string
  api_call <- glue::glue(
         base,
         track_id)
  # GET the API call
  api_result <- httr::GET(api_call, add_headers(Authorization = HeaderValue), 
                                    add_headers("Accept: application/json"),
                                    add_headers("Content-Type: application/json"))
  
  # get the result in a JSON format
  json_result <- httr::content(api_result, "text", encoding="UTF-8")
  # flatten result
  json_result_flat <- jsonlite::fromJSON(json_result, flatten = T)
  
  track_features <- json_result_flat %>% as_tibble() %>% 
    select(danceability:tempo, duration_ms:time_signature) %>% 
    rename_all(~ str_c("feature_", .x))
  
  spotify_track_features <- tibble(track_features)

  spotify_track_features
}

# get_track_features("6KuXb26rHuRy3ZDse1VRmx")
```

### Using these neat ol functions

First we will get the id for each album and artist. These are needed to query the database further.

Not working perfectly...

One way to do this would be that if the thing fails, remove the dash (-) from the album query and nest that within the possibly.


```{r}
df <- df %>% 
    mutate(spotify_album_artist_ids = map(video_album_query, possibly(get_album_id, "Failed"))) 

df <- df %>% 
    unnest(spotify_album_artist_ids)
```

Next we must get the artist information


```{r}
df <- df %>%
    # this removes the ones that didn't get artist ids in the first step.
    filter(is.na(spotify_album_artist_ids)) %>% 
    mutate(spotify_artist_data = map(spotify_artist_id, possibly(get_artist_data, "Failed")))

df <- df %>% 
    unnest(spotify_artist_data)
```

Now to get the information about the songs on the albums

```{r}
df <- df %>% 
    mutate(spotify_album_data = map(spotify_album_id, possibly(get_album_data, "Failed"))) 

df <- df %>% 
  unnest(spotify_album_data)
```

```{r}
df <- df %>% 
    mutate(spotify_track_features = map(track_id, possibly(get_track_features, "Failed"))) 

df <- df %>% 
    unnest(spotify_track_features)
```

```{r}
# write_rds(df, "data/nice_nice_nice_data_compress.rds", compress = "gz")

```


Mutate to get the median or mean of the features?

```{r}
df %>% 
  group_by(video_id) %>% 
  mutate(danceability_mean = mean(danceability),
         danceability_var = var(danceability)) %>% select(video_id, danceability, danceability_mean, danceability_var)


```



```{r}
df <- df %>% nest(data = c(track_name, track_id, track_explicit, danceability, energy, 
    key, loudness, mode, speechiness, acousticness, instrumentalness, 
    liveness, valence, tempo, duration_ms, time_signature, spotify_track_features)) %>% 
  distinct(video_id, .keep_all = T)

write_rds(test_1, "data/audio_features_small.rds")

```


### Getting images of thumbnails

```{r}
df <- read_rds("data/nice_nice_nice_data_compress.rds")

colnames(df)

# we have some missing score data so we will filter it out.
df <- df %>% 
  filter(!is.na(score))

df <- df %>%
  group_by(video_id) %>% 
  mutate(across(track_explicit:time_signature, median)) %>% 
  ungroup() %>% 
  distinct(video_id, .keep_all = T)

```


