---
title: "Cleaning and data processing/ feature engineering"
author: "JJayes"
date: "29/06/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
# library(reticulate)
```



Getting subtitles using python

```{r}
# version <- "3.7.4"
# # install_python(version = version)
# virtualenv_create("my-environment", python_version = version)
# use_virtualenv("my-environment", required = TRUE)
# 
# # installing the package needed for getting the transcripts
# virtualenv_install("my-environment", "youtube_transcript_api")

```

Things to get from video description.

Could maybe do these in a recipe so that I can deploy it via Github Actions and do a CI thing. Would be a fun way to learn recipes. Maybe not the most stable though and relies on the fact that he will continue to structure his descriptions in such a way that I can extract the information methodologically. 

- score
- statistics (views, comments, etc.)
- date
- genre
- record company
- duration

```{r}
tbl <- read_rds("data/album_reviews_raw_added_tags.rds")

tbl %>% skimr::skim()

```



### EDA

```{r}
tbl <- tbl %>% 
    # the \n before it is to correct for the song called 10/10 by Rex Orange County
    mutate(score_raw = str_extract(snippet.description, "\n[0-9]/10|\n10/10|CLASSIC"),
           score = parse_number(score_raw)) 

tbl %>% 
    count(score_raw, sort = T)

tbl %>% 
    select(score, score_raw) %>% 
    arrange(desc(score))

tbl %>% 
    select(score, score_raw, snippet.description) %>% 
    arrange((score))

tbl %>% 
    ggplot(aes(score)) +
    geom_histogram()

tbl %>% filter(score == 10) %>% pull(snippet.description)

tbl %>% 
    filter(snippet.title == "Rex Orange County - Pony ALBUM REVIEW") %>% 
    select(snippet.description) %>% view()

```

Statistics

```{r}
tbl <- tbl %>% 
    mutate(across(starts_with("statistics"), as.numeric))

tbl %>% 
    ggplot(aes(statistics.viewCount)) +
    geom_density()

```

Date

```{r}
tbl <- tbl %>% 
    mutate(published_date = lubridate::date(snippet.publishedAt))

tbl %>% 
    ggplot(aes(published_date, score)) +
    geom_jitter() +
    geom_smooth(method = "lm")

tbl %>% 
    ggplot(aes(published_date, statistics.viewCount)) +
    geom_point() +
    geom_smooth() +
    scale_y_log10(labels = scales::number_format())

tbl %>% 
    ggplot(aes(published_date, statistics.commentCount)) +
    geom_point() +
    geom_smooth() +
    scale_y_log10(labels = scales::number_format())

```

Duration

```{r}
tbl <- tbl %>%
    mutate(duration = lubridate::duration(contentDetails.duration)) 

tbl %>% 
    ggplot(aes(published_date, duration)) +
    geom_point() +
    geom_smooth()

tbl %>% 
    arrange(desc(duration)) %>% head() %>% view()

```

Tags

```{r}
# tbl %>% 
#     select(snippet.tags) %>% 
#     mutate(tags = paste(unlist(snippet.tags), collapse = ";"))

review_list <- tbl %>%
    filter(contentDetails.caption == "true") %>% 
    select(video_id)

# review_list %>% write.csv(., file = "data/video_ids.csv", row.names = F)

```

### Transcipts

testing with the small data set

```{r}
ts <- read.csv("data/test_2.csv")

ts <- ts %>% as_tibble()

ts %>% 
    pull(X0, X1)

ts <- ts %>% 
    select(-X) %>% 
    mutate(across(starts_with("X"), ~ str_remove(.x, "\\{\\'text\\':")),
           across(starts_with("X"), ~ str_remove(.x, ", \\'start':.*")),
           # now to remove the opening quote '
           across(starts_with("X"), ~ str_remove(.x, "^ '")),
           # to remove ending quote '
           across(starts_with("X"), ~ str_remove(.x, "'$")),
           # now to remove the opening double quote "
           across(starts_with("X"), ~ str_remove(.x, "^ \\\"")),
            # to remove ending double quote "
           across(starts_with("X"), ~ str_remove(.x, "\\\"$"))) %>% 
    unite(text, starts_with("X"), sep = " ") %>% 
    mutate(text = str_squish(text),
           text = str_remove_all(text, "\\\""),
           text = str_remove_all(text, "NA"),
           text = str_squish(text))


```

Big data set!

```{r}
ts <- read_csv("data/transcripts_from_album_reviews.csv")

ts <- ts %>% as_tibble()

ts <- ts %>% 
    select(-A) %>% 
    mutate(across(starts_with("X"), ~ str_remove(.x, "\\{\\'text\\':")),
           across(starts_with("X"), ~ str_remove(.x, ", \\'start':.*")),
           # now to remove the opening quote '
           across(starts_with("X"), ~ str_remove(.x, "^ '")),
           # to remove ending quote '
           across(starts_with("X"), ~ str_remove(.x, "'$")),
           # now to remove the opening double quote "
           across(starts_with("X"), ~ str_remove(.x, "^ \\\"")),
            # to remove ending double quote "
           across(starts_with("X"), ~ str_remove(.x, "\\\"$"))) %>% 
    unite(text, starts_with("X"), sep = " ") %>% 
    mutate(text = str_squish(text),
           text = str_remove_all(text, "\\\""),
           text = str_remove_all(text, "NA"),
           text = str_squish(text))

tbl_2 <- tbl %>% bind_cols(ts)

tbl_2 %>% 
    select(text)

# write_rds(tbl_2, "data/transcripts_filtered_and_data.rds")

```


```{r}
library(tidytext)

words <- tbl_2 %>% 
    unnest_tokens(word, text) %>% 
    select(video_id, snippet.title, word)


words <- words %>% 
    anti_join(stop_words) 

words %>% 
    count(word, sort = T) %>% 
    head(100) %>% view()
```

Effect of week?

```{r}
df %>% 
    mutate(week = week(published_date),
           year = year(published_date)) %>%
    group_by(week) %>% 
    mutate(mean_score = mean(score, na.rm = T)) %>%
    ggplot(aes(week, mean_score)) +
    geom_point() +
    geom_line() +
    geom_smooth()

df %>% 
    mutate(week = week(published_date),
           year = year(published_date)) %>%
    group_by(week) %>% 
    ggplot(aes(week, score, group = week)) +
    geom_boxplot()

df %>% 
    mutate(week = week(published_date),
           year = year(published_date)) %>%
    group_by(week) %>% 
    ggplot(aes(week, score)) +
    geom_jitter() +
    geom_smooth()

df %>% 
    mutate(dow = lubridate::day(published_date),
           year = year(published_date)) %>%
    group_by(dow) %>% 
    ggplot(aes(dow, score)) +
    geom_jitter() +
    geom_smooth()
```

Can easily make this into a ridge-line plot

```{r}
df %>% 
    mutate(dow = lubridate::wday(published_date, label = T),
           year = year(published_date)) %>%
    group_by(dow) %>% 
    ggplot(aes(dow, score, group = dow)) +
    geom_boxplot() 

df %>% 
    mutate(dow = lubridate::wday(published_date, label = T),
           year = year(published_date)) %>%
    group_by(dow) %>% 
    ggplot(aes(score)) +
    geom_density() +
    facet_wrap(~ dow)

df %>% 
    mutate(dow = lubridate::wday(published_date, label = TRUE),
           year = year(published_date)) %>%
    count(dow) %>% 
    mutate(dow = fct_rev(dow)) %>% 
    ggplot(aes(n, dow, fill = dow)) +
    geom_col()

```

