---
title: "Website Scraper"
author: "JJayes"
date: "29/06/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(glue)

library(httr)
library(jsonlite)

```

## Purpose

Query API for Youtube to get the captions and the descriptions from the Needle Drop album reviews.

We need to get a list of all of the uploads.

Then we need to filter these to get only the album reviews.

```{r}
key <- "AIzaSyBHGmTJ2uLeMsIjBUN3jN7G3RSjozkaq8k"

user_id <- "theneedledrop"  # Username
base <- "https://www.googleapis.com/youtube/v3/"

```



```{r}
# Construct the API call
api_params <- 
  paste(paste0("key=", key), 
        paste0("forUsername=", user_id), 
        "part=snippet,contentDetails,statistics",
        sep = "&")

api_call <- paste0(base, "channels", "?", api_params)
api_result <- GET(api_call)
json_result <- content(api_result, "text", encoding="UTF-8")
```

```{r}
# Process the raw data into a data frame
channel.json <- fromJSON(json_result, flatten = T)
channel.df <- channel.json$items %>% as_tibble()

# get playlist id for uploads
channel.df %>% 
    select(contentDetails.relatedPlaylists.uploads)

playlist_id <- channel.df %>% 
    select(contentDetails.relatedPlaylists.uploads) %>% as.character()

```


Get all videos from uploads, call it upload.df.

```{r}
# temporary variables
nextPageToken <- ""
upload.df <- NULL
pageInfo <- NULL
# Loop through the playlist while there is still a next page
while (!is.null(nextPageToken)) {
  # Construct the API call
  api_params <- 
    paste(paste0("key=", key), 
          paste0("playlistId=", playlist_id), 
          "part=snippet,contentDetails,status",
          "maxResults=50",
          sep = "&")
  
  # Add the page token for page 2 onwards
  if (nextPageToken != "") {
    api_params <- paste0(api_params,
                         "&pageToken=",nextPageToken)
  }
  
  api_call <- paste0(base, "playlistItems", "?", api_params)
  api_result <- GET(api_call)
  json_result <- content(api_result, "text", encoding="UTF-8")
  upload.json <- fromJSON(json_result, flatten = T)
  
  nextPageToken <- upload.json$nextPageToken
  pageInfo <- upload.json$pageInfo
  
  curr.df <- as.data.frame(upload.json$items)
  if (is.null(upload.df)) {
    upload.df <- curr.df
  } else {
    upload.df <- bind_rows(upload.df, curr.df)
  }
}

upload_tbl <- upload.df %>% as_tibble()

upload_tbl %>% head() %>% view()
```

Get statistics about each video

```{r}
video.df<- NULL
# Loop through all uploaded videos
for (i in 1:nrow(upload.df)) {
  # Construct the API call
  video_id <- upload.df$contentDetails.videoId[i]
  api_params <- 
    paste(paste0("key=", key), 
          paste0("id=", video_id), 
          "part=id,statistics,contentDetails",
          sep = "&")
  
  api_call <- paste0(base, "videos", "?", api_params)
  api_result <- GET(api_call)
  json_result <- content(api_result, "text", encoding="UTF-8")
  video.json <- fromJSON(json_result, flatten = T)
  
  curr.df <- as.data.frame(video.json$items)
  
  if (is.null(video.df)) {
    video.df <- curr.df
  } else {
    video.df <- bind_rows(video.df, curr.df)
  }
}  


video_tbl <- video.df %>% as_tibble()

video.df

video_tbl %>% head() %>% view()

tbl <- upload_tbl %>% left_join(video_tbl, by = "id")

tbl %>% filter(snippet.title == "The Magnetic Fields - 50 Song Memoir ALBUM REVIEW") %>% select(id)

# write_rds(tbl, "data/raw_data_from_yt.rds")
```


Trying to get captions

```{r}
# Construct the API call
id <- "VVV0N2Z3QWhYRHkzb05GVEF6RjJvOFB3LktGR28zU1dPbEtv"

api_params <- 
  paste("onBehalfOf=j0nathanjayes%40gmail.com",
        paste0("key=", key), 
        sep = "&")

api_call <- paste0(base, "captions/", id, "?", api_params)
api_result <- GET(api_call)
json_result <- content(api_result, "text", encoding="UTF-8")
```

```{r}
# Process the raw data into a data frame
channel.json <- fromJSON(json_result, flatten = T)
channel.df <- channel.json$items %>% as_tibble()
```






Rewriting the function to get the data about each video

```{r}
# Loop through all uploaded videos
for (i in 1:nrow(upload.df)) {
  # Construct the API call
  video_id <- upload.df$contentDetails.videoId[i]
  api_params <- 
    paste(paste0("key=", key), 
          paste0("id=", video_id), 
          "part=id,statistics,contentDetails",
          sep = "&")
  
  api_call <- paste0(base, "videos", "?", api_params)
  api_result <- GET(api_call)
  json_result <- content(api_result, "text", encoding="UTF-8")
  video.json <- fromJSON(json_result, flatten = T)
  
  curr.df <- as.data.frame(video.json$items)
  
  if (is.null(video.df)) {
    video.df <- curr.df
  } else {
    video.df <- bind_rows(video.df, curr.df)
  }
}
```


```{r}
tbl <- tbl %>%
  mutate(video_id = str_remove(snippet.thumbnails.default.url, "https://i.ytimg.com/vi/"),
         video_id = str_remove(video_id, "/default.jpg"))

tbl %>% 
  select(video_id)
```


```{r}
video_id <- "6kWWLOampOM"

get_video_data <- function(video_id){
  
  base <- "https://www.googleapis.com/youtube/v3/"
  
  key <- "AIzaSyBHGmTJ2uLeMsIjBUN3jN7G3RSjozkaq8k"
  
  part <- "part=id,statistics,contentDetails,snippet"
  
  api_call <- 
    glue::glue(base,
         "videos?",
         part,
         "&",
         "id=",
         video_id,
         "&",
         "key=",key)

  api_result <- httr::GET(api_call)
  
  json_result <- httr::content(api_result, "text", encoding="UTF-8")
  
  json_result_flat <- jsonlite::fromJSON(json_result, flatten = T)
  
  results <- json_result_flat$items
  
  tags <- json_result_flat$items$snippet.tags[[1]] %>% toString() %>% as_tibble() %>% rename(tags = value)
  
  results <- results %>% dplyr::as_tibble() %>% 
    select(-snippet.tags)
  
  results <- results %>% bind_cols(tags)
    
  
}

test <- get_video_data("6kWWLOampOM")


```

Redoing this to get the tags right...

```{r}
tbl <- read_rds("data/raw_data_from_yt.rds")

tbl <- tbl %>%
  mutate(video_id = str_remove(snippet.thumbnails.default.url, "https://i.ytimg.com/vi/"),
         video_id = str_remove(video_id, "/default.jpg"))


list_of_album_reviews <- tbl %>% 
  select(video_id, snippet.title) %>% 
  filter(str_detect(snippet.title, "ALBUM REVIEW"))

album_reviews <- list_of_album_reviews %>% 
  mutate(video_data = map(video_id, get_video_data))

album_reviews <- album_reviews %>% 
  select(-snippet.title) %>% 
  unnest(video_data)


write_rds(album_reviews, "data/album_reviews_raw_added_tags.rds")

```

